Information Disclosure in Dynamic Innovation Contests

### 2025-06-13 paper/Paper.tex
Update Paper.tex

After careful evaluation, we find that contests reporting accuracy-based scores (i.e., values between 0 and 1 on the leaderboard) tend to yield a higher success rate in identifying two focal players.
Therefore, all contests used in this study are restricted to those where the leaderboard displays accuracy scores.
To ensure consistency with the theoretical definition of the performance gap variable $y_t$ and $\hat{y}_t$, we further transform the raw leaderboard accuracy values using the logit (log-odds) function: 
\begin{equation}\label{eq-leaderboard-transform}
y_t = a \cdot \log\left(\frac{p_t}{1-p_t}\right), \quad p_t\in[0.5, 1)
\end{equation}
where $p_t$ is the leaderboard score, and $a$ is a tune parameter for the normality of $y_t$.\footnote{
For different contest data, parameter $a$ is different. 
 The goal is to make the transformed data more consistent with the normality assumption in (\ref{eq-state-dynamics}).
}
The logit function is S-shaped, with the key property that as the accuracy $p_t$ approaches 1, each marginal improvement in $p_t$ results in a disproportionately large increase in the transformed value $y_t$. 
This feature aligns with the intuition that it becomes increasingly difficult to improve performance near the upper bound, making such gains more informative in competitive settings.

@@

{\color{red}
It is important to note that, since our analysis relies on normality assumptions which heavily relies on the form of data transformation (\ref{eq-leaderboard-transform}). 
We conduct a series of normality tests on the sample points $(\hat{y}_t^c - y_t^c)$ for each contest $c$.
}

>>>>

After careful evaluation, we find that contests reporting accuracy-based scores (i.e., values between 0 and 1 on the leaderboard) tend to yield a higher success rate in identifying two focal players.
Therefore, all contests used in this study are restricted to those where the leaderboard displays accuracy scores.
To ensure consistency with the theoretical definition of the performance gap variable $y_t$ and $\hat{y}_t$, we further transform the raw leaderboard accuracy values using the logit (log-odds) function: 
\begin{equation}\label{eq-leaderboard-transform}
y_t = a \cdot \log\left(\frac{p_t}{1-p_t}\right), \quad p_t\in[0.5, 1)
\end{equation}
where $p_t$ is the leaderboard score, and $a$ is a tune parameter for the normality of $y_t$.\footnote{
For different contest data, parameter $a$ is different. 
 The goal is to make the transformed data more consistent with the normality assumption in (\ref{eq-state-dynamics}).
In practise, we just pick $a = 1$. 
}
The logit function is S-shaped, with the key property that as the accuracy $p_t$ approaches 1, each marginal improvement in $p_t$ results in a disproportionately large increase in the transformed value $y_t$. 
This feature aligns with the intuition that it becomes increasingly difficult to improve performance near the upper bound, making such gains more informative in competitive settings.

@@

It is important to emphasize that the normality assumption in this setting is induced by the transformation defined in equation~(\ref{eq-leaderboard-transform}). 
However, the current transformation form is adopted for simplicity, and does not guarantee strict normality—especially under extreme contest data—which may reduce the validity of our MLE.\footnote{So far, only half of the contest data can pass the Shapiro-Wilk test. }
Future work should explore more reliable transformation methods to better approximate the assumed distribution.
